Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-06 journal paper/content/sec-intro.tex
Minor formatting thing.

While amenable to simulations, the \ExptsModel appears difficult to analyze. This is for several reasons:
%
(i) intricate feedback loop from performance to reputations to users to performance;
%
(ii) mean reputation, most connected to our intuition, is sometimes a bad predictor in competition (see Sections~\ref{sec:isolation} and~\ref{sec:revisited}); and
%
(iii)
mathematical tools from regret-minimization would only produce ``asymptotic" results, which do not seem to suffice. Given the theoretical results on the \TheoryModel, and the fact that we are in the realm of stylized economic models that provide mathematical intuition about the world, we believe that resolving first-order theoretical questions about the \ExptsModel would not add much value to this paper.

@@

\newpage
\ascomment{Left the previous version for now (from Guy).}

>>>>

While amenable to simulations, the \ExptsModel appears difficult to analyze. This is for several reasons:
%
(i) intricate feedback loop from performance to reputations to users to performance;
%
(ii) mean reputation, most connected to our intuition, is sometimes a bad predictor in competition (see Sections~\ref{sec:isolation} and~\ref{sec:revisited}); and
%
(iii)
mathematical tools from regret-minimization would only produce ``asymptotic" results, which do not seem to suffice. Given the theoretical results on the \TheoryModel, and the fact that we are in the realm of stylized economic models, we believe that resolving first-order theoretical questions about the \ExptsModel would not add much value to this paper.

@@

\newpage
\section{STUFF FROM THE PREVIOUS VERSION}

\ascomment{Left the previous version for now (from Guy).}
